\chapter{Conclusions}
\label{chap:conclusions}

This thesis set out to close part of the marketing-quality gap between large brands and the independent retailers that compete with them, by building a production-grade cloud platform that turns a shop's product photographs, brand identity and a stream of real-world context signals into ready-to-publish marketing assets. The platform was delivered as a cross-platform React Native client backed by an ASP.NET Core service on Microsoft Azure, with three technical contributions sitting on top of the architectural baseline: a multi-stage daily recommendation engine grounded in retrieved context and a fine-tuned writer, a hybrid generative--deterministic catalogue pipeline that preserves product fidelity pixel for pixel, and a tiled super-resolution path that turns model-resolution assets into print-ready PDFs.

The thread running through the contributions is that the gap between an off-the-shelf model and an output a small retailer is willing to publish is rarely closed by a bigger model. It is closed by the protocol that sits around the model: a typed prompt chain in the recommendation case, an outline-as-contract in the catalogue case, and fixed paper sizes with a hard $300\,$dpi target in the print case. In each instance the deterministic machinery around the AI call is what makes the AI call's output reliable enough to ship.

\section{Future improvements}
\label{sec:future-work}

Several extensions would meaningfully strengthen the platform.

\begin{itemize}
    \item \emph{Self-serve billing via Stripe.} The current credit ledger is fed only by administrator grants, which is acceptable for a research deployment but not for paying customers. Replacing the admin-grant flow with Stripe Checkout for one-off credit packs and Stripe Billing for monthly subscription tiers, with webhooks reconciling each successful charge against the existing ledger, would close the loop from sign-up to paid usage without operator intervention. The credit ledger's atomic debit-and-record discipline makes Stripe webhooks a natural fit, as failed charges and refunds map directly to ledger reversals.
    \item \emph{Engagement feedback loop.} Pulling per-post performance metrics from the connected social channels (reach, engagement, click-through) and feeding them back into the recommendation engine as a per-shop signal would let future ideas favour the patterns that have already worked for that retailer. This turns the engine from a stateless suggester into one that learns the shop's audience over time.
    \item \emph{Per-shop writer adaptation.} Periodic LoRA refreshes on each shop's accepted-versus-rejected ideas would let the writer model converge to the shop's own voice without retraining the base model. The infrastructure for hot-swappable adapters is already in place from the writer-stage fine-tuning described in Chapter~\ref{chap:contributions}.
    \item \emph{Short-form video generation.} Extending the asset pipeline beyond stills to $5$--$15\,$s vertical video clips would unlock the formats that now dominate Instagram Reels, TikTok and YouTube Shorts. The hybrid contract translates naturally: the model designs the moving scene, the deterministic compositor places the real product photo and any required text overlay onto each frame.
    \item \emph{Scheduled and automated publishing.} The recommendation engine already produces a daily slate; the missing piece is letting the retailer mark an accepted idea for auto-publication at a chosen day and time, with retry on platform failure. This would turn the platform from an authoring tool into a complete daily marketing operation that runs without further intervention.
    \item \emph{Print-on-demand fulfilment.} The print pipeline currently produces a paper-sized PDF that the retailer must print themselves. A partnership with a print-on-demand provider would let the A4 export become an in-app order for a hundred shipped flyers, which is the form in which most independent retailers actually need physical marketing material.
    \item \emph{Controlled benchmark for the recommendation engine.} The qualitative evaluation in Chapter~\ref{chap:testing} relies on an LLM-as-judge protocol and a small human pairwise pass. A more rigorous study --- a frozen evaluation set sized for statistical power, blind human raters drawn from the target retailer audience, and a per-failure-mode breakdown --- would let the platform make defensible quality claims rather than only directional ones.
\end{itemize}

\noindent Taken together these directions extend the platform along the two axes that matter most for a small-retailer product: the commercial axis (self-serve billing, scheduled publishing, print fulfilment) that turns it into a service a shop can rely on without operator help, and the quality axis (engagement feedback, per-shop adaptation, controlled benchmarking) that lets the underlying AI keep getting better at the specific shop in front of it.
