\chapter{Introduction}
\label{chap:introduction}

\section{Context}

Small and independent retailers, including local craft shops, neighbourhood boutiques, and family-run restaurants, face a structural disadvantage when it comes to marketing. Larger competitors employ in-house design teams, marketing departments, and creative agencies that produce a steady stream of polished promotional material throughout the year. Independent shops, by contrast, rarely have the time, budget, or expertise to produce the kind of professional visual content that today's customers have come to expect on social media, in physical storefronts, and in printed catalogs. The result is a visible quality gap between large brands and the local businesses that compete with them, and this gap continues to widen as larger competitors invest aggressively in digital marketing.

In the last few years, generative artificial intelligence has begun to close part of this gap. Modern image-generating models can produce visuals of striking quality from a short text prompt, and conversational language models can draft promotional copy on demand. In principle, these tools should be transformative for small retailers; in practice, however, the leap from a general-purpose model to a polished, brand-consistent advertisement is far from trivial. Models occasionally produce visually appealing but factually inaccurate renderings of a product, struggle to incorporate a retailer's exact branding (logo, colour palette, typography, tone of voice), and require careful prompting that most non-technical users are not equipped to perform. Equally important, they do not, on their own, decide \emph{when} a campaign should be run, or \emph{what theme} would resonate with a particular local audience on a particular day.

The platform presented in this thesis was developed against this backdrop. It treats marketing automation as more than a single image-generation step: it gathers a retailer's brand profile, organises a library of their products, monitors a small set of real-world contextual signals such as weather, holidays, and local events, and uses these inputs to drive a generation pipeline tailored to produce high quality marketing assets. The platform is designed as a cross-platform solution, ensuring a smooth experience across both desktop web browsers and mobile devices, and is hosted on the Microsoft Azure cloud so that it can be operated as a real production service rather than as a controlled experiment.

\section{Objectives}

Concretely, this thesis pursues the following objectives:

\begin{itemize}
    \item To design and implement a cross-platform application that automates the production of marketing assets directly from a retailer's product photographs and shop information.
    \item To enable retailers to assemble their product library with minimal manual effort, either by uploading their own photographs and removing the background automatically through an AI model, or by searching a curated reference database by visual similarity to a sample photo or by name.
    \item To develop a recommendation engine that suggests fresh marketing themes on a daily basis, grounded in real-world contextual signals such as weather, holidays, and local events, so that the platform is useful as an everyday tool rather than a one-off generator.
    \item To investigate and implement a hybrid generation strategy in which a generative model designs the surrounding scene while the retailer's actual product photograph is preserved through deterministic post-processing, addressing a well-known limitation of current models in faithfully reproducing specific real-world objects, and to extend this pipeline with a high-resolution rendering path that produces print-ready posters suitable for being displayed physically outside the shop.
    \item To package the resulting platform as a production-grade cloud service deployed on Microsoft Azure, in order to demonstrate that the proposed approach is viable beyond a controlled experimental setting.
    \item To reflect on the trade-offs between fully generative pipelines and hybrid generative-deterministic ones, and to identify the conditions under which each approach is appropriate.
\end{itemize}

\section{Thesis Structure}

The remainder of this thesis is organised as follows. \textit{Chapter 2} reviews the theoretical foundations on which the system is built, including modern image-generating models, prompt engineering, retrieval-augmented generation, and techniques for measuring visual similarity between images. \textit{Chapter 3} describes the overall architecture of the platform and explains how it is deployed on the Microsoft Azure cloud. \textit{Chapter 4} details the implementation, with a particular focus on the recommendation engine and the hybrid generation technique that together constitute the main technical contributions of this work. \textit{Chapter 5} describes the testing strategy, covering automated suites for architectural correctness and the offline evaluation protocol applied to the language-model output. \textit{Chapter 6} concludes with a summary of the contributions and a number of directions for future work.

During the preparation of this work the author used ChatGPT in order to improve the language and readability of the thesis. After using ChatGPT, the author reviewed and edited the content as needed and takes full responsibility for the content of the thesis.
